\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fontawesome} % icons

%===================
% Color & Link Theme
%===================
\definecolor{customblue}{HTML}{0A66C2} % LinkedIn Blue
\hypersetup{
    colorlinks=true,
    urlcolor=customblue,
    linkcolor=black
}
\titleformat{\section}{\color{customblue}\bfseries\uppercase}{\thesection}{1em}{}[\titlerule]

\begin{document}

%===================
% Header
%===================
\begin{center}
    {\Huge \textbf{Abiud Wamalwa}}\\
    Bungoma, Kenya \\
    \faEnvelope\ \href{mailto:abiudwamalwa1979@gmail.com}{abiudwamalwa1979@gmail.com} \quad
    \faPhone\ +254 792 129 479 \\
    \faGithub\ \href{https://github.com/waabiud}{GitHub} \quad
    \faLinkedin\ \href{https://linkedin.com/in/abiud-wamalwa}{LinkedIn} \quad
    \faGlobe\ \href{https://wamalwa.co.ke}{Portfolio}
\end{center}

%===================
% Professional Summary
%===================
\section*{Professional Summary}
Motivated Mathematics and Computing student specializing in Full Stack Development and Data Analytics. Proven ability to build responsive e-commerce platforms and dynamic web apps. Eager to contribute technical skills and creativity to a forward-thinking organization while continuing to grow as a software engineer.

%===================
% Skills
%===================
\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} JavaScript, Python, Java, C, SQL, R
    \item \textbf{Frontend:} HTML5, CSS3, ReactJS, Bootstrap
    \item \textbf{Backend:} Node.js, Express.js, RESTful APIs
    \item \textbf{Databases:} MongoDB, MySQL
    \item \textbf{Tools:} Git, GitHub, Linux, AWS, Apache, Nginx, LaTeX
    \item \textbf{Soft Skills:} Communication, Critical Thinking, Problem Solving, Decision Making
\end{itemize}

%===================
% Certifications
%===================
\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item \faCheckCircle\ CompTIA A++ — \textit{2022}
    \item \faAws\ AWS Certified Cloud Architect — \textit{2023}
\end{itemize}

%===================
% Projects
%===================
\section*{Projects}
\textbf{E-Commerce Website (MERN Stack)} \\
Built a full-featured e-commerce platform with user authentication, payment integration (M-Pesa), shopping cart, and admin dashboard.

\textbf{Online Voting System (Java + MySQL)} \\
Secure web-based voting app with role-based login, encrypted data storage, and real-time vote tallying.

\textbf{Music Player Web App (MERN)} \\
Feature-rich app with genres, speed control, and light/dark modes; demonstrates UI/UX skills and functional programming.

%===================
% Work Experience
%===================
\section*{Work History}
\textbf{Frontend Developer (Freelance)} \hfill \textit{Upwork} \\
\textit{March 2023 – Present}
\begin{itemize}[leftmargin=*]
    \item Built responsive web and e-commerce applications using ReactJS, JavaScript, and Bootstrap.
    \item Integrated M-Pesa and PayPal for secure payment handling.
    \item Implemented shopping carts, order tracking, and login systems with clean and optimized code.
\end{itemize}

%===================
% Education
%===================
\section*{Education}
\textbf{BSc in Mathematics and Computing} \\
Kaimosi Friends University, Kenya \\
\textit{September 2023 – Present}

%===================
% Achievements & Leadership
%===================
\section*{Achievements and Leadership}
\begin{itemize}[leftmargin=*]
    \item Contributed to open-source projects on GitHub (\href{https://github.com/waabiud}{waabiud})
    \item Participated in tech meetups and hackathons
\end{itemize}

%===================
% Languages
%===================
\section*{Languages}
English: Fluent \\
Swahili: Fluent

%===================
% Interests
%===================
\section*{Interests}
AI and Machine Learning, Coding, Outdoor Activities, Community Involvement

%===================
% References
%===================
\section*{References}

\textbf{Wafula Samuel} \\
Software Engineer — Fraym \\
\faPhone\ +254 727 007 405 \\
\faEnvelope\ \href{mailto:samziggler@gmail.com}{samziggler@gmail.com}

\vspace{0.5em}

\textbf{Dickson Makulia} \\
Network Administrator — Maruway Networks \\
\faPhone\ +254 713 005 403 \\
\faEnvelope\ \href{mailto:makulia.dickson@gmail.com}{makulia.dickson@gmail.com}

\end{document}
